### 2011-01-26 paper/platformDetails.tex
minor edit

The quadruped robot was printed on the Objet
Connex 500 3-D Printing System. It weights 1884 g and measures approximately
15 centimeters from leg to leg in the crouch position depicted in
\figref{robot_close.jpg}. There are a total of 9 AX-12+ Dynamixel
Servomotors: 4 outer leg joint
servos, 4 inner leg joint servos, and a final servo at the center "hip" of the
robot (displayed in \figref{topdown.png}). The robot has an on-board computer running Linux. 
The lower level drivers are in C and the system is implemented in Python.

>>>>

The quadruped robot was printed on the Objet
Connex 500 3-D Printing System. It weights 1884 g and measures approximately
15 centimeters from leg to leg in the crouch position depicted in
\figref{robot_close.jpg}. There are a total of 9 AX-12+ Dynamixel
Servomotors, displayed in \figref{topdown.png}: 4 outer leg joint
servos, 4 inner leg joint servos, and a final servo at the center "hip" of the
robot. The robot has an on-board computer running Linux. 
The lower level drivers are in C and the system is implemented in Python.
